Inequalities Witnessing Quantum Incompatibility in The Triangle Scenario

### 2016-10-20 document/main.tex
Some progress

% === Commonly re-occurring symbols ===
\newcommand{\hgraph}{\mathcal{H}}
\newcommand{\graph}{\mathcal{G}}
\newcommand{\nodes}{\mathcal{N}}
\newcommand{\weights}{\mathcal{W}}
\newcommand{\edges}{\mathcal{E}}
\newcommand{\trans}{\mathcal{T}}
\newcommand{\ind}{\mathcal{I}}
\newcommand{\netperm}{\Pi}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\ancestralindep}{\perp}
\newcommand{\valprod}{\times}
\newcommand{\bigvalprod}{\prod}
\newcommand{\com}{\mathrel{\Yright\hspace{-0.2em}\Yleft}}
\newcommand{\ext}{\mathrel{\Yleft}}
\newcommand{\res}{\mathrel{\Yright}}
\newcommand{\gep}{\varphi}
\newcommand{\gp}{\Phi}
\newcommand{\geo}{\omega}
\newcommand{\go}{\Omega}
\newcommand{\mscenario}{\mathcal{M}}
\newcommand{\jointvar}{\mathcal{J}}
\newcommand{\mset}[1]{\gamma^{#1}}
\newcommand{\extmset}[1]{\Gamma^{#1}}
\newcommand{\supp}[1]{\si\br{#1}}

@@

\setoperator{Pa} % Parents of a node
\setoperator{Ch} % Children of a node
\setoperator{An} % Ancestry of a node
\setoperator{Sub} % subgraph
\setoperator{AnSub} % Ancestral subgraph
\setoperator{Ext} % Extension of outcomes
\setoperator{Com} % Compatible equivalence relation
\setoperator{Nec} % Necessary nodes
\setoperator{UnNec} % Unnecessary nodes
\setoperator{Inj} % injectable sets
\setoperator{ImInj} % images of the injectable sets
\setoperator{PreInj} % Pre-injectable sets
\setoperator{ImPreInj} % images of the Pre-injectable sets
\setoperator{Aut} % graph automorphism
\setoperator{Orb} % Group Orbits
\setoperator{Perm} % Permutation group
\setoperator{Out} % Outcome space
\setoperator{Dom} % Domian
% \setoperator{Dom} % Domian
% \setoperator{Dom} % Domian

@@

    \section{Introduction}
    \todo[TC]{Discuss why the marginal problem is important.}
    \section{Definitions \& Notation}
    \comment[TC]{This entire section should be integrated into the body when logical to do so.}
    \begin{definition}
        Following common notation used in \cite{Fritz_2011}, we use the notation $\bs{k} = \bc{1, \ldots, k}$ to be a finite index set. Moreover, when referencing a finite set with $k$ elements, we can write,
        \[ A_{\bs{k}} \defined \bc{A_i}_{i \in \bs{k}} = \bc{A_1, \ldots, A_k} \]
    \end{definition}
    \begin{definition}
        \label{def:outcome_space}
        Each random variable $v$ has a set of possible outcomes which are labeled by \term{outcome labels} $O_v$. The set of all outcomes themselves is its \term{outcome space} and is represented by the set of all functions from $v$ to $O_v$\footnote{Using functional language for outcome events is necessary for a sheaf-theoretic treatment of contextuality \cite{Abramsky_2011}.},
        \[ \Out{v} \defined \bc{f : \bc{v} \to O_v} \]
        Each of these functions has a singular domain ($v$) and thus can be concisely written in a compact form $\bc{v \mapsto o}$ where $o \in O_v$ represents some generic outcome label. Each function $f$ should be interpreted as the \textit{event} that $v$ obtains the outcome $o$, as well as the function that takes $v$ to $o$ $\bc{v \mapsto f\br{v} = o}$. Evidently $\Out{v}$ is isomorphic to $O_v$, and in many cases the two can be considered equivalent; however we make this particular semantic distinction now in preparation of \cref{sec:symmetry}.
    \end{definition}

    \begin{definition}
        % This notation generalizes to more than one variable. Letting $V = \bc{v_1, v_2}$, we define $\Out{V}$ to be the set of all joint valuations of $v_1$ and $v_2$.
        % Where the valuation product between outcome spaces is defined as follows,\footnote{At this level, a valuation product behaves analogously to a Cartesian product. However in \cref{def:extendable_set}, we define the a valuation product between outcomes and outcomes spaces.}
        % \[ \Out{V} = \Out{\bc{v_1, v_2}} \defined \bc{f : \bc{v_1, v_2} \to \bc{O_{v_1}, O_{v_2}} \mid f\br{v_i} \in O_{v_i}, i \in \bc{1,2}}  \]
        As a natural generalization, when considering a larger set of random variables $V = \bc{v_i}_{i \in \bs{k}}$ we define the joint outcome space in an analogous way,
        \[ \Out{V} \defined \bc{f: \bc{v_i}_{i \in \bs{k}} \to \bc{O_{v_i}}_{i \in \bs{k}} \mid \forall i \in \bs{k} : f\br{v_i} \in O_{v_i} } \eq \label{eq:outcome_space}\]
        Each outcome $f$ can be compactly represented as a set of mappings over each element of $V$.
        \[ f = \bc{v_1 \mapsto f\br{v_1}, \ldots, v_k \mapsto f\br{v_k}} = \bc{v_i\mapsto f\br{v_i}}_{i \in \bs{k}} \]
        The domain of $f$ refers to the set of random variables it valuates and is denoted as $\Dom{f}$. If $f \in \Out{V}$, then $\Dom{f} = V$.
        % Where the joint outcome labels are elements of a Cartesian product,
        % \[ O_V \defined O_{v_1} \times \cdots \times O_{v_{\abs{V}}}  \]

        % And a generic, unspecified joint outcome in $\Out{V}$ is written as $\outc{V}$ in a similar fashion to \cref{def:outcome_space} and is represented by a tuple of individual outcomes.
        % \[ \outc{V} \defined \br{\outc{v_1}, \ldots, \outc{v_{k}}} = \br{\outc{v}}_{v \in V} \eq \label{eq:outcomespace}\]
        % It is important to note that the ordering of events in \cref{eq:outcomespace} is irrelevant.
         % The definition of a valuation product can also be extended to outcomes themselves. Let $A$ and $B$ be sets of random variables and let $\outc{A} \in \Out{A}$ and $\outc{B} \in \Out{B}$. If $$
    \end{definition}

    \begin{example}
        Interpreting $f \in \Out{V}$ as an \textit{event} or \textit{outcome} on $V$, a probability distribution $\prob[V]$ over $V$ will assign a non-negative probability $\prob[V][f]$ to $f$. Let $V = \bc{v_1, v_2}$ with each $v \in V$ having $3$ distinct outcomes $O_v = \bc{0,1,2}$. Furthermore let $f \in \Out{V}$ be the outcome $\br{v_1 \mapsto 2, v_2 \mapsto 1}$. The following class of notations will be considered interchangeable,
        \[ \prob[V][f] = \prob[v_1, v_2][f] = \prob[][v_1 \mapsto f_1\br{v_1}, v_2 \mapsto f_2\br{v_2}] = \prob[][v_1 \mapsto 2, v_2 \mapsto 1] = \prob[v_1v_2][21] \]
        Each of which should be read as ``the probability that $v_1$ gets outcome $2$ AND $v_2$ gets outcome $1$''.
    \end{example}

    \begin{remark}
        \label{rem:domain_dist}
        In each of the above notations, $\prob[V]$ always represents a probability distribution over the \textit{domain} of $f \in \Out{V}$. In cases where the subscript is omitted, it should be assumed to be over the domain of $f$.
        \[ \prob[V][f] = \prob[\Dom{f}][f] = \prob[][f] \]
    \end{remark}

    \begin{definition}
        \label{def:restriction}
        Let $V = \bc{v_1, \ldots, v_k}$ be a set of random variables and $W \subseteq V$ be a subset of $V$. Moreover, let $f \in \Out{V}$ be a joint outcome over $V$; assigning a unique label to each variable in $V$. The \term{restriction of $f$ onto $W$} (denoted $f|_{W} \in \Out{W}$) is the outcome of $\Out{W}$ that \textit{agrees} with each of $f$'s assignments for variables in $W$.
        \[ \forall v \in W : f\br{v} = f|_{W}\br{v} \]
    \end{definition}

    \begin{definition}
        \label{def:outcome_compatible}
        Consider two sets of random variables $V$ and $W$ and two specific outcomes $f_V \in \Out{V}$ and $f_W \in \Out{W}$. The outcomes $f_V$ and $f_W$ are said to be \term{compatible} if they agree on their valuations of $V \cap W$. Compatibility will be denoted with `$\com$'.
        \[ f_V \com f_W \iff {f_V}|_{V\cap W} = {f_W}|_{V\cap W} \]
        Compatibility is a reflexive and symmetric, but \textit{not} transitive. There are two cases when compatibility is transitive; whenever $V \cap W = \emptyset$ or $V = W$. Whenever $V \cap W = \emptyset$, $f_V$ and $f_W$ can be said to be \textit{trivially} compatible. Moreover if $V = W$, compatibility becomes ordinary equivalence,
        \[ V = W \quad \textrm{and} \quad f_V \com f_W \iff f_V = f_W \]
    \end{definition}

    \begin{definition}
        \label{def:extendable}
        Let $f_V \in \Out{V}$ and $f_W \in \Out{W}$ be outcomes of $V$ and $W$ respectively as in \cref{def:outcome_compatible}. If $f_V$ and $f_W$ are compatible, and $W \subseteq V$ then $f_W$ is said to be \term{extendable} to $f_V$ and is denoted `$\ext$'.
        \[ f_W \ext f_V \iff f_W \com f_V \quad \textrm{and} \quad W \subseteq V \iff {f_W} = {f_V}|_{W} \]
        The dual language is also appropriate: $f_W$ is a \term{restriction} of $f_V$ (denoted $f_V \res f_W$) if and only if $f_W$ is extendable to $f_V$. If $f_W \ext f_V$ then there exists a unique element $f_{V \setminus W} \in \Out{V \setminus W}$ such that $f_V$ can be reconstructed by gluing together $f_{V \setminus W}$ and $f_W$.
        \[ \forall v \in V : f_V\br{v} = \begin{cases}
            f_W\br{v} & v \in W \\
            f_{V\setminus W}\br{v} & v \in V \setminus W
        \end{cases}  \]
    \end{definition}

    \begin{remark}
        The notation `$g \com h$' is used to indicate compatibility between $g \in \Out{V}$ and $h \in \Out{W}$ because of the following observation; $g$ and $h$ are compatible if and only if extensions of some outcome $f \in \Out{V \cap W}$.
        \[ g \com h \iff \exists f \in \Out{V \cap W} \mid g \res f \ext h \]
        In fact, such an $f$ is uniquely defined,
        \[ \forall v \in V \cap W : f\br{v} = g\br{v} = g\br{v} \]
    \end{remark}

    \begin{definition}
        \label{def:extendable_set}
        The set of all extendable outcomes of $f \in \Out{W}$ into $V$ is called the \term{extendable set of $f$ into $V$} and can be written as,
        \[ \Ext[V]{f} \defined \bc{g \in \Out{V} \mid f \ext g} \subseteq \Out{V} \]
        The extendable set of $f$ into $V$ is the subset of outcomes in $\Out{V}$ that \textit{agree} with $f$ about valuations for variables in $W$.
    \end{definition}

    \begin{example}
        Let $W = \bc{a, b}$ and $V = \bc{a, b, c}$ be two sets of random variables. Clearly $W \subseteq V$; a prerequisite for extendability. Further impose that the outcome labels for each variable are the same: $O_a = O_b = O_c = \bc{0,1,2}$. As an example, let $f = \bc{a \mapsto f\br{a} = 1, b \mapsto f\br{b} = 2} \in \Out{W}$; $f$ is extendable to the outcome $g = \bc{a \mapsto g\br{a} = 1, b \mapsto g\br{b} = 2, c \mapsto g\br{c} = 1} \in \Out{V}$, and the extendable set of $f$ into $V$ is,
        \[ \Ext[V]{f} = \Ext[a,b,c]{a \mapsto 1, b \mapsto 2} = \bc{\bc{a \mapsto 1, b \mapsto 2, c \mapsto 0}, \bc{a \mapsto 1, b \mapsto 2, c \mapsto 1}, \bc{a \mapsto 1, b \mapsto 2, c \mapsto 2}} \]
    \end{example}

    % \begin{definition}
    %     Two outcomes $\outc{V_1}$ and $\outc{V_2}$ over two distinct sets of random variables $V_1$ and $V_2$ are called \term{accordant} or \textit{compatible} if they are mutually realizable. In terms of extendable sets, $\outc{V_1}$ and $\outc{V_2}$ are accordant if there exists an outcome $\outc{V_1 \cup V_2} \in O_{V_1 \cup V_2}$ such that,
    %     \[ \outc{V_1}, \outc{V_2} \subseteq \outc{V_1 \cup V_2}  \]
    %     Accordance between two outcomes is the \textit{opposite} of exclusive.
    % \end{definition}

    \begin{definition}
        \label{def:graph}
        A \term{graph} is an ordered tuple $\br{\nodes, \edges}$ of \textit{nodes} and \textit{edges} respectively where the nodes can represent any object and the edges are pairs of nodes. For convenience of notation, one defines an index set over the nodes denoted $\ind_\nodes$.
        \[ \nodes = \bc{n_i \mid i \in \ind_\nodes} \quad \edges = \bc{\bc{n_j, n_k} \mid j,k \in \ind_\nodes} \]
    \end{definition}

    \begin{definition}
        \label{def:directed_graph}
        A \term{directed graph} $\graph$ is an ordered tuple $\br{\nodes, \edges}$ of \textit{nodes} and \textit{edges} respectively where the nodes can represent any object and the edges are \textit{ordered} pairs of nodes. For convenience of notation, one defines an index set over the nodes denoted $\ind_\nodes$.
        \[ \nodes = \bc{n_i \mid i \in \ind_\nodes} \quad \edges = \bc{n_j \to n_k \mid j,k \in \ind_\nodes} \]
    \end{definition}

    \begin{definition}
        \label{def:graph_terms}
        The following definitions are common language in directed graph theory. Let $n, m \in \nodes$ be example nodes of the graph $\graph$.
        \begin{itemize}
            \item The \term{parents of a node}: $\Pa[\graph]{n} \defined \bc{m \mid m \to n}$
            \item The \term{children of a node}: $\Ch[\graph]{n} \defined \bc{m \mid n \to m}$
            \item The \term{ancestry of a node}: $\An[\graph]{n} \defined \bigcup_{i\in\mathbb{W}} \Pa[\graph][i]{n}$ where $\Pa[\graph][i]{n} \defined \Pa[\graph]{\Pa[\graph][i-1]{n}}$ and $\Pa[\graph][0]{n} = n$
        \end{itemize}
        All of these terms can be generalized to sets of nodes $N \subseteq \nodes$ through union over the elements,
        \begin{itemize}
            \item The \term{parents of a node set}: $\Pa[\graph]{N} \defined \bigcup_{n\in N}\Pa[\graph]{n}$
            \item The \term{children of a node set}: $\Ch[\graph]{N} \defined \bigcup_{n\in N}\Ch[\graph]{n}$
            \item The \term{ancestry of a node set}: $\An[\graph]{N} \defined \bigcup_{n\in N}\An[\graph]{n}$
        \end{itemize}
        Moreover, an \term{induced subgraph} of $\graph$ due to a set of nodes $N \subseteq \nodes$ is the graph composed of $N$ and all edges $e \in \edges$ of the original graph that are contained in $N$.
        \[ \Sub[\graph]{N} \defined \br{N, \bc{e_i \mid i \in \ind_\edges, e_i \subseteq N}}\]
        An \term{ancestral subgraph} of $\graph$ due to $N \subseteq \nodes$ is the induced subgraph due to the ancestry of $N$.
        \[ \AnSub[\graph]{N} \defined \Sub[\graph]{\An[\graph]{N}} \]
    \end{definition}

    \begin{definition}
        \label{def:dag}
        A \term{directed acyclic graph} or \term{DAG} $\graph$ is an directed graph \cref{def:directed_graph} with the additional property that no node $n$ is in its set of \term{ancestors}.
        \[ \forall n \in \nodes : n \notin \bigcup_{i\in\mathbb{N}} \Pa[\graph][i]{n}\]
        Notice the difference between using the natural numbers $\mathbb{N}$ to distinguish \textit{ancestors} from \textit{ancestry}.
    \end{definition}

    \begin{definition}
        A \term{causal structure} is simply a DAG with the extra classification of each node into one of two categories; the \term{latent nodes} and \term{observed nodes} denoted $\nodes_L$ and $\nodes_O$. The latent nodes correspond to random variables that are either hidden through some fundamental process or cannot/will not be measured. The observed nodes are random variables that are measurable. Every node is either latent or observed and no node is both:
        \[ \nodes_L \cap \nodes_O = \emptyset \qquad \nodes_L \cup \nodes_O = \nodes \]
    \end{definition}

    \begin{definition}
        The \term{product distribution} of two disjoint distributions $\prob[V]$ and $\prob[W]$ (where $V \cap W = \emptyset$) is denoted as usual with $\prob[V] \times \prob[W]$ and is defined as,
        \[ \forall f \in \Out{V \cup W} : \br{\prob[V] \times \prob[W]}\br{f} \defined \prob[V][f|_{V}]\cdot\prob[W][f|_{W}] \]
        A product distribution of $k$ mutually disjoint distributions is defined as,
        \[ \prod_{i\in\bs{k}} \prob[V_i] \defined \br{\prob[V_1] \times \cdots \times \prob[V_k]} \]
    \end{definition}

    \begin{definition}
        The \term{marginalization} of a distribution $\prob[V]$ to a distribution over $W \subseteq V$ is denoted $\sum_{V \setminus W} \prob[V]$ and is defined such that,
        \[ \forall f \in \Out{W} : \br{\sum_{V \setminus W} \prob[V]}\br{f} \defined \sum_{g \in \Ext[V]{f}} \prob[V][g] \]
    \end{definition}
    \comment[TC]{How many definitions do I need to write??}

>>>>

% === Commonly re-occurring symbols ===
\newcommand{\hgraph}{\mathcal{H}}
\newcommand{\graph}{\mathcal{G}}
\newcommand{\nodes}{\mathcal{N}}
\newcommand{\weights}{\mathcal{W}}
\newcommand{\edges}{\mathcal{E}}
\newcommand{\trans}{\mathcal{T}}
\newcommand{\ind}{S}
\newcommand{\inhibit}{\mathcal{I}}
\newcommand{\netperm}{\Pi}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\ancestralindep}{\perp}
\newcommand{\valprod}{\times}
\newcommand{\bigvalprod}{\prod}
\newcommand{\com}{\mathrel{\Yright\hspace{-0.2em}\Yleft}}
\newcommand{\ext}{\mathrel{\Yleft}}
\newcommand{\res}{\mathrel{\Yright}}
\newcommand{\gep}{\varphi}
\newcommand{\gp}{\Phi}
\newcommand{\geo}{\omega}
\newcommand{\go}{\Omega}
\newcommand{\mscenario}{\mathcal{M}}
\newcommand{\jointvar}{\mathcal{J}}
\newcommand{\mset}{\gamma}
\newcommand{\extmset}{\Gamma}
\newcommand{\supp}[1]{\si\br{#1}}
\newcommand{\kone}{\mathbf{1}}
\newcommand{\kzer}{\textcolor{gray}{0}}

@@

\setoperator{Pa} % Parents of a node
\setoperator{Ch} % Children of a node
\setoperator{An} % Ancestry of a node
\setoperator{Sub} % subgraph
\setoperator{AnSub} % Ancestral subgraph
\setoperator{Ext} % Extension of outcomes
\setoperator{Com} % Compatible equivalence relation
\setoperator{Nec} % Necessary nodes
\setoperator{UnNec} % Unnecessary nodes
\setoperator{Inj} % injectable sets
\setoperator{ImInj} % images of the injectable sets
\setoperator{PreInj} % Pre-injectable sets
\setoperator{ImPreInj} % images of the Pre-injectable sets
\setoperator{Aut} % graph automorphism
\setoperator{Orb} % Group Orbits
\setoperator{Perm} % Permutation group
% \setoperator{Out} % Outcome space
\newcommand{\Sect}[1]{\s{S}\br{#1}} % Outcome space
\newcommand{\Dom}[1]{\s{D}\br{#1}} % Domian
% \setoperator{Dom} % Domian
% \setoperator{Dom} % Domian

@@

    \section{Introduction}
    \todo[TC]{Mention Bell's work} \\

    \todo[TC]{Violations of inequalities correspond to resources} \\

    \todo[TC]{Finding inequalities is hard} \\

    \todo[TC]{Causal inference is a great lens to answer these questions} \\

    \todo[TC]{Demonstrated the usefulness of the inflation technique} \\

    \todo[TC]{Definite Extension procedure} \\

    \todo[TC]{Optimizations against inequalities} \\

    \section{Compatibility, Contextuality and the Marginal Problem}
    \label{sec:comp_con_mp}

    \subsection{Preliminary Notions}
    \label{eq:comp_con_mp_notions}
    A reoccurring motif of these discussions will be a set of marginal probability distributions $\bc{\prob[V_1], \ldots, \prob[V_k]}$. In agreement with~\cite{Fritz_2011} we adopt the following definitions and notation.

    \begin{definition}
        \label{def:marginal_model}
        A set of random variables $\jointvar = \bc{v_1, \ldots, v_n}$ is referred to as the \term{joint random variables} when denoted with a $\jointvar$. A subset of joint variables $V \subset \jointvar$ is called \term{marginal context}. A collection of marginal contexts is called the \term{marginal scenario}\footnote{Rigorously speaking as defined by~\cite{Fritz_2011}, a marginal scenario forms an \textit{abstract simplicial complex} where it is required that $V' \in \mscenario$ whenever $V' \subseteq V \in \mscenario$. Throughout this document, we only consider the \textit{maximal marginal scenario}; restricting our focus to the largest contexts in the marginal scenario $\forall i,j \in 1, \ldots, k: V_i \not \subseteq V_j$.} and is denoted $\mscenario$\footnote{It is also assumed that the marginal scenario covers the joint variables $\jointvar = \bigcup_{i = 1}^{k} V_i$.}.
        \[ \mscenario \defined \bc{V_1, \ldots, V_k \mid V_i \subseteq \jointvar} \]
        Additionally, the set of probability distributions $\bc{\prob[V_1], \ldots, \prob[V_k]}$ over the marginal scenario is called a \term{marginal model} is compactly denoted $\prob^{\mscenario}$.
    \end{definition}
    A specific marginal model $\prob^{\mscenario}$ for a marginal scenario $\mscenario$ abstractly represents a set of measurements or observations made on a physical system. Associated with the physical system are physical models or causal structures.

    \begin{definition}
        A \term{causal structure} is a directed acyclic graph (DAG) $\graph = \br{\nodes, \edges}$ with the extra distinction between two classes of nodes: the \term{latent nodes} $\nodes_L$ and \term{observed nodes} $\nodes_O$.
    \end{definition}
    The latent nodes of a causal structure correspond aim to represent completely general hidden variables that are hidden by some fundamental process or cannot be measured due to other limitations. The observed nodes represent random variables that are measurable and in practice will be observed as a collection of marginal contexts $\mscenario$. Any observation over this particular marginal scenario is expressible as a marginal model $\prob^{\mscenario}$. The field of causal inference aims to answer the looming question: \text{Is the observed marginal model compatible with the hypothesized causal structure?} \\

    In order to determine if a given marginal model $\prob^{\mscenario}$ is compatible with a causal structure $\graph$, a formal notion of \textit{compatibility} is warranted; first for a single marginal distribution $\prob[V]$ and then for a complete marginal model $\prob^{\mscenario} = \bc{\prob[V_1], \ldots, \prob[V_k]}$.

    \begin{definition}
        A set of \term{causal parameters} for a particular causal structure $\graph$ is the specification of a conditional distribution for every node $n \in \nodes$ given its parents in $\graph$.
        \[ \bc{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes} \eq \label{eq:def:casual_param}\]
    \end{definition}

    \begin{definition}
        \label{def:compatible}
        A marginal distribution $\prob[V]$ is \term{compatible} with a causal structure $\graph$ if there exists a \textit{choice} of causal parameters such that $\prob[V]$ can be \textit{recovered} from the following series of operations:
        \begin{enumerate}
            \item Obtain a joint probability distribution over \textit{all} nodes of of the causal structure using the chosen casual parameters: $\prob[\nodes] = \prod_{n \in \nodes} \prob[n \mid \Pa[\graph]{n}]$.
            \item Marginalize over the latent nodes of $\graph$: $\prob[\nodes_O] = \sum_{\nodes_L} \prob[\nodes]$.
            \item Finally marginalize over the observed nodes not in $V$ to obtain $\prob[V]$: $\prob[V] = \sum_{\nodes_O \setminus V} \prob[\nodes_O]$
        \end{enumerate}
        If it is not possible for $\prob[V]$ to be recovered for \textit{any} choice of causal parameters, then $\prob[V]$ is \term{incompatible}. To generalize, a marginal model $\prob^{\mscenario}$ is compatible with $\graph$ if each distribution $\prob[V] \in \prob^{\mscenario}$ can be made compatible by the \textit{same} choice of causal parameters; otherwise it is incompatible.
    \end{definition}

    There are two reasons why a given marginal model $\prob^{\mscenario}$ would be deemed incompatible. One possibility is that the marginal model $\prob^{\mscenario}$ does not admit a joint distribution $\prob[\jointvar]$ such that it is impossible for requirement 3 of \cref{def:compatible} to hold\footnote{It is typical for $\nodes_O = \jointvar$. At the very least, it is demanded that $\jointvar \subseteq \nodes_O$.}. Alternatively, it could be possible that a joint distribution $\prob[\jointvar]$ exists but can not factor into causal parameters as per requirement 1 of \cref{def:compatible}. The former point-of-failure, namely the non-admission of a joint distribution, will be principle focus of this paper. Colloquially, the existence (or non-existence) of a joint distribution is referred to as \textit{the marginal problem}.

    \begin{definition}
        \label{def:marginal_problem}
        \term{The Marginal Problem:} Given a marginal model $\prob^{\mscenario} = \bc{\prob[V_1], \ldots, \prob[V_k]}$ marginal to the joint variables $\jointvar = \bigcup_{i} V_i$, does there exist a joint distribution $\prob[\jointvar]$ such that each given distribution $\prob[V_i]$ can be obtained by marginalizing $\prob[\jointvar]$?
        \[ \forall V \in \mscenario : \prob[V] = \sum_{\jointvar \setminus V} \prob[\jointvar] \eq \label{eq:def:marginal_problem}\]
        Following definition 2.3 in~\cite{Fritz_2011}, a marginal model is said to be \term{contextual} if it \textit{does not} admit a joint distribution $\prob[\jointvar]$ and \term{non-contextual} otherwise.
    \end{definition}

    There are two perspectives that can be taken when trying to answer the marginal problem. The first comes as stated by \cref{def:marginal_problem}; when inured with a particular marginal model $\prob^{\mscenario}$, can you construct a joint distribution that satisfies \cref{def:marginal_problem}? Alternatively and more abstractly, when provided a marginal \textit{mscenario} $\mscenario$ what is the set of all marginal models that are (non-)contextual? To facilitate future discussions, let $\s{NC}$ denote the set of marginal models that are non-contextual (admitting a joint distribution) and let $\s{C}$ denote the set of contextual marginal models. It becomes desirable to identifying conditions that constrain either $\s{NC}$ or $\s{C}$. We will continue to refer to a \term{complete solution marginal problem} as a finite set of necessary and sufficient conditions able to discern if a given marginal model $\prob^{\mscenario}$ is in $\s{NC}$ or $\s{C}$. These constraints typically take the form of linear inequalities over probabilities $\prob^{\mscenario}$.

    \begin{definition}
        A \term{$\s{NC}$-inequality} $I_{\mscenario}$ for a marginal scenario $\mscenario$ is a probabilistic inequality that is obeyed for every non-contextual marginal model $\prob^{\mscenario}$.
    \end{definition}

    In the \cref{sec:linear_program}, we will explore and briefly mention existing techniques for completely (or partially) solving the marginal problem. The basis of understanding being that \cref{eq:def:marginal_problem} is a \textit{linear} operation. In certain circumstances, \cref{eq:def:marginal_problem} can be represented as a matrix operation.

    \todo[TC]{Maybe define the possibilistic marginal problem for later} \\

    \subsection{Casting the Marginal Problem as a Linear Program}
    \label{sec:linear_program}

    Heretofore, our discussions of compatibility, contextuality and the marginal problem have be completely general, making no reference to the nature of the outcomes of the random variables $\jointvar$; whether they be discrete or continuous, finite or unbounded, or otherwise. \todo[TC]{It is entirely possible to obtain complete solutions to the marginal problem for continuous and unbounded measure spaces using entropic inequalities. [Elaborate and reference]} In this paper we restrict our attention to finite outcomes. In particular, we will focus on marginal scenarios that are finite but have a large number of outcomes. To assist with the subsequent analysis, we recall some familiar notions of probability theory together with new terminology and notation. \\

    \subsubsection{Sections}
    To every discrete random variable $v$ there corresponds a prescribed set of \term{outcomes} $O_v$. We also define the set of all \term{sections over $v$} $\Sect{v}$\footnote{Technically $\Sect{v}$ can be called a \textit{sheaf} but we neglect to introduce that terminology here.} to be the set of all functions $s : \bc{v} \to O_v$ each representing the event that a measurement on $v$ was made where $s\br{v} \in O_v$ was observed.
    \[ \Sect{v} \defined \bc{s : \bc{v} \to O_v} \label{eq:outcome_space} \]
    Making the unfamiliar distinction between sections $s$ and outcomes in $O_v$ might seem pedantic. Evidently, $\Sect{v}$ and $O_v$ have a one-to-one correspondence. There is rarely any harm in referring synonymously to either as outcomes. Nonetheless, a sheaf-theoretic treatment of contextuality~\cite{Abramsky_2011} demands the distinction.
    Specifically for this work, the distinction becomes essential for our discussion and exploit of marginal symmetries in \cref{sec:symmetry}. As a natural generalization we define the tuple sections for collection of random variables $V = \bc{v_1, \ldots, v_n}$ in a parallel manner,
    \[ \Sect{V} \defined \bc{s: V \to O_{V} \mid \forall i : s\br{v_i} \in O_{v_i} } \eq \label{eq:outcome_space}\]
    Each section $s$ can be compactly represented as a set of mappings over each element of $V$.
    \[ s = \bc{v_1 \mapsto s\br{v_1}, \ldots, v_k \mapsto s\br{v_k}} = \bc{v_i\mapsto s\br{v_i}}_{i = 1}^{k} \]
    The domain $\Dom{s}$ of an section $s$ is the set of random variables it valuates, i.e. if $s \in \Sect{V}$, then $\Dom{s} = V$.
    \begin{example}
        Let $s \in \Sect{V}$ be a section over $V$, a probability distribution $\prob[V]$ over $V$ will assign a non-negative probability $\prob[V][s]$ to $s$. Let $V = \bc{v_1, v_2}$ with each $v \in V$ having $3$ distinct outcomes $O_v = \bc{0,1,2}$. Furthermore let $f \in \Sect{V}$ be the section $\br{v_1 \mapsto 2, v_2 \mapsto 1}$. Then the following notations are interchangeable,
        \[ \prob[][s] = \prob[\Dom{s}][s] = \prob[V][s] = \prob[v_1, v_2][s] = \prob[][v_1 \mapsto s_1\br{v_1}, v_2 \mapsto s_2\br{v_2}] = \prob[][v_1 \mapsto 2, v_2 \mapsto 1] = \prob[v_1v_2][21] \]
        Each of which should be read as ``the probability that $v_1$ got outcome $2$ and $v_2$ got outcome $1$''
    \end{example}
    \begin{definition}
    \label{def:section_restriction}
    For every $W \subseteq V$ and $s \in \Sect{V}$, the \term{restriction of $s$ onto $W$} (denoted $s|_{W} \in \Sect{W}$) is the section in $\Sect{W}$ that \textit{agrees} with each of $s$'s assignments for variables in $W$.
    \[ \forall v \in W : s|_{W}\br{v} = s\br{v} \]
    \end{definition}
    \begin{definition}
    \label{def:section_compatible}
    The sections $s_{V} \in \Sect{V}$ and $s_{W} \in \Sect{W}$ are said to be \term{compatible} sections if they agree on their valuations of $V \cap W$. Compatibility will be denoted with the infix `$\com$'.
    \[ s_{V} \com s_{W} \iff {s_{V}}|_{V\cap W} = {s_{W}}|_{V\cap W} \]
    \end{definition}
    \begin{definition}
    \label{def:section_extendable}
    It $s_V \in \Sect{V}$ and $s_W \in \Sect{W}$ compatible sections and $W \subseteq V$ then $s_W$ is said to be \term{extendable} to $s_V$. Extendability will be denoted with the infix `$\ext$'.
    \[ s_W \ext s_V \iff s_W \com s_V, W \subseteq V \]
    Extendability is dual to the notion of a \term{restriction} of $s_V$; $s_V$ can be restricted to $s_W$ ($s_V \res s_W$) if and only if $s_W$ is extendable to $s_V$.
    \end{definition}

    \begin{remark}
        The notation `$s \com t$' is used to indicate compatibility between $s \in \Sect{V}$ and $t \in \Sect{W}$ because of the following observation: $s$ and $t$ are compatible if and only if they are extensions of some outcome $r \in \Sect{V \cap W}$.
        \[ s \com t \iff \exists r \in \Sect{V \cap W} \mid s \res r \ext t \]
        In fact $r$ is uniquely defined.
        \[ \forall v \in V \cap W : r\br{v} = s\br{v} = t\br{v} \]
    \end{remark}

    \begin{definition}
        \label{def:extendable_set}
        The set of all extendable sections of $s \in \Sect{W}$ into $V$ is called the \term{extendable set of $s$ into $V$}.
        \[ \Ext[V]{s} \defined \bc{g \in \Sect{V} \mid s \ext g} \subseteq \Sect{V} \]
        The extendable set of $s$ into $V$ is the subset of sections in $\Sect{V}$ that \textit{agrees} with $s$ about valuations for variables in $W$.
    \end{definition}

    \begin{example}
        Let $W = \bc{a, b}$ and $V = \bc{a, b, c}$ be two sets of random variables. Clearly $W \subseteq V$; a prerequisite for extendability. Further impose that the outcome labels for each variable are the same: $O_a = O_b = O_c = \bc{0,1,2}$. As an example, let $s = \bc{a \mapsto s\br{a} = 1, b \mapsto s\br{b} = 2} \in \Sect{W}$. The extendable set of $s$ into $V$ is,
        \[ \Ext[V]{s} = \Ext[a,b,c]{a \mapsto 1, b \mapsto 2} = \bc{\bc{a \mapsto 1, b \mapsto 2, c \mapsto 0}, \bc{a \mapsto 1, b \mapsto 2, c \mapsto 1}, \bc{a \mapsto 1, b \mapsto 2, c \mapsto 2}} \]
    \end{example}

    For every marginal scenario $\mscenario = \bc{V_1, \ldots, V_k}$, it is useful to put special emphasis on the \term{joint sections} $\Sect{\jointvar}$. Similarly we define the \term{context sections} $\bc{\Sect{V} \mid V \in \mscenario}$. Finally, we elect to define the disjoint union of all context sections are called the \term{marginal sections} and by an abuse of notation we will denote this disjoint union as $\Sect{\mscenario}$.
    \[ \Sect{\mscenario} = \coprod_{V \in \mscenario} \Sect{V} \]
    Each marginal section $m \in \Sect{\mscenario}$ has a domain $\Dom{m} = V$ for some $V \in \mscenario$.
    \subsubsection{Linear Programs}
    \label{sec:linear_programs}
